% --- LaTeX CV Template - S. Venkatraman ---

% --- Set document class and font size ---

\documentclass[letterpaper, 11pt]{article}

% --- Package imports ---

\usepackage{hyperref, enumitem, longtable, amsmath, array}
\usepackage{fontawesome5}  % For social media icons
\usepackage{graphicx}     % For image handling

% --- Page layout settings ---

% Set page margins
\usepackage[left=0.7in, right=0.8in, bottom=.8in, top=0.8in, headsep=0in, footskip=.2in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.2}

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}


% --- Page formatting settings ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=MidnightBlue, urlcolor=MidnightBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% Define font size and color for section headings
\newcommand{\headingfont}{\Large\color{OliveGreen}}

% --- CV section settings ---

% Note: each section of this table (Education, Awards, Publications etc.) is 
% stored in a two-column table. The left-hand column is narrow (1 inch) and is 
% meant to store dates. The right-hand column is wide (5.2 inches) and stores 
% the main text.  Sections in which each entry might have multiple lines 
% (e.g., Education) are stored in a 'SectionTable' environment). Sections in 
% which each entry might just have one line are stored in a 'SectionTableSingleSpace'
% environment. The only difference between the two environments is the line 
% spacing between each entry. Both environments take one argument, which is the
% title of the section. See main document for how these environments are used.

% Define settings for left-hand column in which dates are printed
\newcolumntype{R}{>{\raggedleft}p{1in}}

% Define 'SectionTable' environment
\newenvironment{SectionTable}[1]{
	\renewcommand*{\arraystretch}{1.4}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{5.2in}} & #1 \\}
{\end{longtable}\vspace{-.85cm}}

% Define 'SectionTableSingleSpace' environment
\newenvironment{SectionTableSingleSpace}[1]{
	\renewcommand*{\arraystretch}{1.0}
	\setlength{\tabcolsep}{10pt}
	\begin{longtable}{Rp{5.2in}} & #1 \\[0.3em]}
{\end{longtable}\vspace{-.3cm}}

% --- Document starts here ---

\begin{document}

% --- Name and contact information ---

\begin{SectionTable}{\Huge Sky (Kehan) Sheng} & 
skysheng7@gmail.com  $\;\boldsymbol{\cdot}\;$ 
+1 778-681-9736 $\;\boldsymbol{\cdot}\;$ Vancouver, BC, Canada\newline
\socialicon{\faGlobe} \href{https://skysheng.io}{skysheng.io} $\;\boldsymbol{\cdot}\;$
\socialicon{\faLinkedin} \href{www.linkedin.com/in/sky-sheng}{sky-sheng} $\;\boldsymbol{\cdot}\;$
\socialicon{\faGithub} \href{https://github.com/skysheng7}{skysheng7} \newline 
\socialicon{\faGraduationCap} \href{https://scholar.google.com/citations?user=yz-cWVgAAAAJ}{Kehan (Sky) Sheng}
$\;\boldsymbol{\cdot}\;$ 
\socialicon{\faOrcid} \href{https://orcid.org/0000-0001-6442-5284}{0000-0001-6442-5284} 
\end{SectionTable}

% --- Section: Research interests ---
\begin{SectionTable}{\headingfont About Me}
& I'm passionate about using AI to empower marginalized communities and address real-world challenges. As a PhD candidate at University of British Columbia (UBC) animal welfare program, lecturer at UBC Master of Data Science Program, and collaborator at TrustML, I conduct interdisciplinary research bridging \textbf{AI bias}, \textbf{data science}, and \textbf{animal welfare science}. My previous research includes automated dairy cow behavior and disease monitoring. Currently, I explore biases and tranparency issues in generative AI. I believe it's crucial that we don't lose the voices of those not in power and making them invisible behind numeric machines through coded gaze. I strive to make my research fully reproducible and accessible to all.
\end{SectionTable}


% --- Section: Publications ---

\begin{SectionTable}{\headingfont Selected Publications}
& \textit{Note: Full list of publications available \href{https://www.skysheng.io/research/}{here}, and oral presentations available \href{https://www.skysheng.io/speaking/}{here}} \\ [6pt]
2025 & 
\textbf{{The erasure of intensive livestock farming in text-to-image generative AI}} \newline
\textbf{Sheng, K.}, Tuyttens, F.A.M., von Keyserlingk, M.A.G. \newline
\textit{ACM Conference on Fairness, Accountability, and Transparency (ACM FAccT), oral presentation. }\text{\href{https://doi.org/10.48550/arXiv.2502.19771}{https://doi.org/10.48550/arXiv.2502.19771}} \newline
\textit{Note: This work was also presented as poster + lightning talk at Vancouver Vision \& Learning Workshop \@ ICML 2025} \\
2025 &
\textbf{{Redefining Lameness Assessment: Constructing Lameness Hierarchy using Crowd-Sourced Data}} \newline
\textbf{Sheng, K.}, Foris, B., von Keyserlingk, M.A.G., Timbers, T.A., Cabrera, V., Weary, D.M. \newline
\textit{Computers and Electronics in Agriculture. }\text{\href{https://doi.org/10.1016/j.compag.2025.110206}{https://doi.org/10.1016/j.compag.2025.110206}} \\
2024 & 
\textbf{{Redefining dominance calculation: Increased competition flattens the dominance hierarchy in dairy cows}} \newline
\textbf{Sheng, K.}, Foris, B., Krahn, J., Weary, D.M., von Keyserlingk, M.A.G. \newline
\textit{Journal of Dairy Science}, 107(9): 7286-7298. \text{\href{https://doi.org/10.3168/jds.2023-24587}{https://doi.org/10.3168/jds.2023-24587}} \\
2023 & 
\textbf{{Crowd sourcing remote comparative lameness assessments for dairy cattle}} \newline
\textbf{Sheng, K.}, Foris, B., von Keyserlingk, M.A.G., Gardenier, J., Clark, C., Weary, D.M. \newline
\textit{Journal of Dairy Science}, 106(8): 5715-5722. \text{\href{https://doi.org/10.3168/jds.2022-22737}{https://doi.org/10.3168/jds.2022-22737}}\\
2025 & 
\textbf{{AI for One Welfare: the role of animal welfare scientists in developing valid and ethical AI-based welfare assessment tools}} \newline
Foris, B., \textbf{Sheng, K.}, Dürnberger, C., Oczak, M., Rault, J.L. \newline
\textit{Frontiers in Veterinary Science}, 12. \text{\href{https://doi.org/10.3389/fvets.2025.1645901}{https://doi.org/10.3389/fvets.2025.1645901}}\\
2024 & 
\textbf{{Automated, longitudinal measures of drinking behavior provide insights into the social hierarchy in dairy cows}} \newline
Foris, B., Vandresen, B., \textbf{Sheng, K.}, Krahn, J., Weary, D.M., von Keyserlingk, M.A.G. \newline
\textit{JDS Communications}, 5(5): 411-415. \text{\href{https://doi.org/10.3168/jdsc.2023-0487}{https://doi.org/10.3168/jdsc.2023-0487}}\\
2024 & 
\textbf{{Effects of group size on agonistic interactions in dairy cows: a descriptive study}} \newline
Krahn, J., Foris, B., \textbf{Sheng, K.}, Weary, D.M., von Keyserlingk, M.A.G. \newline
\textit{Animal}, 18(3): 101083. \text{\href{https://doi.org/10.1016/j.animal.2024.101083}{https://doi.org/10.1016/j.animal.2024.101083}} \\
\end{SectionTable}

% --- Section: Research Funding ---
\begin{SectionTableSingleSpace}{\headingfont Selected Research Funding \& Awards}
	& \textit{Total research funding secured: \$74,975 CAD. Total scholarship awarded: \$45,756 CAD} \\[6pt]
	& \textit{Full research funding and awards available \href{https://www.skysheng.io/awards/}{here}} \\[6pt]
	2025 &
	ACM Conference on Fairness, Accountability, and Transparency (FAccT) Travel Grant (\$1308.2 USD) \\
	2022 & 
	EAAP Early Career Researcher Award -- \textbf{First Place} in Oral Presentation \\
	2021 -- 2025 &
	Pei-Huang Tung and Tan-Wen Tung Graduate Fellowship (Total: \$19,550 CAD) \\
\end{SectionTableSingleSpace}
	

% --- Section: Teaching experience ---
\begin{SectionTable}{\headingfont Selected Teaching Experience}
& \textit{Full teaching experience available \href{https://www.skysheng.io/teaching/}{here}} \\[6pt]
Fall 2025 & 
\textbf{Lecturer, UBC Master of Data Science Program} \newline 
Teaching two graduate courses: DSCI 522: Reproducible and Trustworthy Data Science Workflows and DSCI 571: Supervised Machine Learning. Designed and taught workshops including \href{http://www.skysheng.io/ai_tools_playground/}{AI Tools Playground: Responsible Use of Generative AI}, \href{https://github.com/skysheng7/linux_command_in_aws_ec2.git}{Linux Command Using Cloud Computing}.\\
Summer 2025 & 
\textbf{Instructor \& Mentor, Data Science Summer Camps at VISST \& UBC} \newline 
Designed and taught \href{http://www.skysheng.io/data_science_for_kids/}{Data Science for Kids Summer Camp} covering AI-assisted programming, statistical inference, data visualization, K-nearest neighbor, and AI ethics. Also mentored participants in \href{https://katieburak.github.io/girls-in-DS/README.html}{Data Science for Girls Summer Camp}. \\
Fall 2024 -- Spring 2025 & 
\textbf{Teaching Assistant, UBC Master of Data Science Program} \newline 
Supported five graduate courses (116 students each): DSCI 525 (Web and Cloud Computing), DSCI 553 (Statistical Inference and Computation II), DSCI 524 (Collaborative Software Development), DSCI 522 (Data Science Workflows), and DSCI 552 (Statistical Inference and Computation I). \\
2022/4 -- 2024/8 &
\textbf{Instructor, \href{https://www.visst.ca/past-camps/machinelearningsummer}{Machine Learning and AI Summer Camp} at VISST} \newline
Taught high school students (11-16 years old) an introduction to machine learning, covering decision trees, computer vision, natural language processing, reinforcement learning, generative AI and AI ethics. \\
\end{SectionTable}

	
% --- Section: Leadership, Community and Volunteer Activities ---
\begin{SectionTable}{\headingfont Selected Leadership, Community and Volunteer Activities}
2021/1 -- present &
\textbf{Student Mentor and Supervisor, UBC} \newline
Mentored 26 undergraduate and graduate students in data science, statistics, computer science, biology, and applied animal biology during PhD studies. Supervised research projects ranging from computer vision and machine learning applications to statistical modeling and R package development. \\
2024/1 &
\textbf{External Reviewer, Dutch Research Council (NWO)} \newline
Assessed research funding application for the Dutch Research Council, with a focus on projects related to computer science and neuroscience. \\
2021/12 -- 2023/5 &
\textbf{Organizer and Coordinator, UBC Animal Welfare Program 25th Anniversary Webinar Series Celebration} \newline
Planned a webinar series to celebrate UBC Animal Welfare Program's 25th Anniversary. Invited alumni to give presentations showcasing their impact on the animal welfare field. \\
2019/3 -- 2020/3 &
\textbf{Student Leader and Ambassador, Agriculture Future of America} \newline
Built a bridge for undergraduate students to connect with industry professionals through strategic networking, leadership development, and career-building initiatives. Represented Agriculture Future of America at various conferences (e.g., Alltech One 19) to negotiate funding and network with industry professionals. \\
2017/12 &
\textbf{Organizer and Speaker Introducer, TED x UW-Madison} \newline
Organized and hosted TEDx UW-Madison with club members, introduced speakers, and worked as an event photographer. \\
\end{SectionTable}

% --- Section: Education ---
\begin{SectionTable}{\headingfont Education}
	2020/9 -- Present & 
	\textbf{University of British Columbia} -- Vancouver, BC, Canada \newline
	\textit{\href{https://awp.landfood.ubc.ca/people/graduate-students/kehan-sheng/}{PhD in Applied Animal Biology X Data Science}} \newline 
	\textit{\href{https://trustml.ubc.ca/profiles/sky-sheng}{Research Collaborator at TrustML}} \newline 
	\textit{Average: 91\%} \\

	2017/9 -- 2020/5 & 
	\textbf{University of Wisconsin - Madison} -- Madison, WI, USA \newline
	\textit{Bachelor of Science in Animal Science, minor in Computer Science} \newline 
	\textit{GPA: 3.97/4.0} \newline
	Honors: Dean's List (2017-2020), Distinctive Scholastic Achievement \\
\end{SectionTable}
	

% --- End of CV! ---

\end{document}





